### 2021-09-05 paper.lagda.tex
paper lagda added

\documentclass{llncs}
\usepackage{hyperref}
\bibliographystyle{splncs04}
%\usepackage{ucs}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{txfonts}
%\usepackage{bbm}
%\usepackage[greek,english]{babel}

% agda.sty wants to use the deprecated utf8x option, which
% many publishers don't like. So we do it ourselves

\usepackage{agda}

\usepackage{proof}

% this stuff is related to the Agda latex backend with inputenc/utf8
% not having heard of many charactersrs...

\usepackage{newunicodechar}
\newunicodechar{∋}{$\ni$}
\newunicodechar{·}{$\cdot$}
\newunicodechar{⊢}{$\vdash$}
\newunicodechar{⋆}{${}^\star$}
\newunicodechar{Π}{$\Pi$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{ƛ}{$\lambdabar$}
\newunicodechar{∅}{$\emptyset$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ϕ}{$\Phi$}
\newunicodechar{ψ}{$\Psi$}
\newunicodechar{ρ}{$\rho$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{σ}{$\sigma$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{∥}{$\parallel$}
\newunicodechar{Λ}{$\Lambda$}
\newunicodechar{₂}{$~_2$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{Θ}{$\Theta$}
\newunicodechar{∘}{$\circ$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{⊧}{$\models$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{η}{$\eta$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{ξ}{$\xi$}
\newunicodechar{₁}{$1$}
\newunicodechar{ℕ}{$\mathbb{N}$}
\newunicodechar{ᶜ}{${}^c$}
\newunicodechar{Φ}{$\Phi$}
\newunicodechar{Ψ}{$\Psi$}
\newunicodechar{⊤}{$\top$}

\newunicodechar{×}{$\times$}
\newunicodechar{ℓ}{\ensuremath{\mathnormal{\ell}}}
\newunicodechar{∣}{\ensuremath{\mathnormal{\|}}}
\newunicodechar{∥}{\ensuremath{\mathnormal{\||}}}
\newunicodechar{₀}{\ensuremath{{}_0}}
\newunicodechar{₁}{\ensuremath{{}_1}}
\newunicodechar{ℚ}{\ensuremath{\mathnormal{\mathbb{Q}}}}
\newunicodechar{ℤ}{\ensuremath{\mathnormal{\mathbb{Z}}}}
\newunicodechar{∷}{\ensuremath{::}}

\usepackage{hyperref}
\usepackage{cleveref}

\author{Guilherme Horta Alvares da Silva}
\email{guilhermehas@hotmail.com}
\title{Making all equalities equal}

\begin{document}

\AgdaHide{
\begin{code}
{-# OPTIONS --cubical --type-in-type #-}

module paper where

-- open import Cubical.Foundations.Prelude
-- open import Cubical.Foundations.Isomorphism
-- open import Cubical.Foundations.Equiv
-- open import Cubical.Foundations.Univalence
-- open import Agda.Primitive
-- open import Cubical.Data.Equality
--
open import Agda.Primitive.Cubical
\end{code}
}

\maketitle

\begin{abstract}

\end{abstract}

\section{Propositional Equality}

In the begin of Agda and in most theorems proves, the equality is given by Martin-Löf's definition:

\begin{code}
module Martin-Löf {ℓ} {A : Set ℓ} where

  data _≡_ (x : A) : A → Set ℓ where
    refl : x ≡ x
\end{code}

This equality is very covenient in proof assistances like Agda, because it is possible to pattern match using them:

\begin{code}
  private variable
    x y z : A

  sym  : x ≡ y → y ≡ x
  sym refl = refl

  trans : x ≡ y → y ≡ z → x ≡ z
  trans refl refl = refl
\end{code}

But the problem of this equality is that it does not handle extensionality and other axioms very well.

\begin{code}
module FunExt {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
  open Martin-Löf

  funExt-Type = {f g : A → B}
    → ((x : A) → f x ≡ g x) → f ≡ g
\end{code}

\section{Cubical Equality}

To solve this problem, Agda adopted cubical type theory that equality is a function from path to types:

\begin{code}
module CubicalEquality {ℓ} {A : Set ℓ} where
  postulate
    PathP : (A : I → Set ℓ) → A i0 → A i1 → Set ℓ

  _≡_ : A → A → Set ℓ
  _≡_ = PathP λ _ → A
\end{code}

From this equality, I will define reflection, symmetry and extensionality:

\begin{code}
module CubicalResults {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
  open import Cubical.Core.Primitives

  private variable
    x y z : A

  refl : x ≡ x
  refl {x = x} = λ _ → x

  sym : x ≡ y → y ≡ x
  sym p i = p (~ i)

  funExt : {f g : A → B}
    → ((x : A) → f x ≡ g x) → f ≡ g
  funExt p i x = p x i
\end{code}

The operator \AgdaBound{~_} revert the interval. If the interval \AgdaBound{i} goes from
\AgdaBound{i0} to \AgdaBound{i1}, the interval \AgdaBound{~ i} goes from \AgdaBound{i1} to \AgdaBound{i0}.

\section{Leibniz equality}

Leibniz equality is defined in this way:
If \AgdaBound{a} is equal to \AgdaBound{b}, then for every propositional \AgdaBound{P}, if \AgdaBound{P a},
then \AgdaBound{P b}.
The main idea is that if both values are equal, then they are seen equal for every angle.

\begin{code}
module Leibniz {ℓ} {ℓ'} {A : Set ℓ} where
  _≐_ : (a b : A) → Set
  a ≐ b = (P : A → Set ℓ') → P a → P b
\end{code}

%\subsection{}

\section*{Acknowledgements}

\bibliography{bibliography}
\end{document}

### 2021-09-09 paper.lagda.tex
nix build compiling pdf
changed unicode and added more code

@@
-\documentclass{llncs}
+\documentclass{article}
 \usepackage{hyperref}
@@
 \newunicodechar{∋}{$\ni$}
-\newunicodechar{·}{$\cdot$}
+% \newunicodechar{·}{$\cdot$}
 \newunicodechar{⊢}{$\vdash$}
@@
 \newunicodechar{Λ}{$\Lambda$}
+\newunicodechar{₁}{$~_0$}
+\newunicodechar{₁}{$~_1$}
 \newunicodechar{₂}{$~_2$}
@@
 \newunicodechar{ξ}{$\xi$}
-\newunicodechar{₁}{$1$}
 \newunicodechar{ℕ}{$\mathbb{N}$}
@@
 \newunicodechar{⊤}{$\top$}
+\newunicodechar{≐}{$\doteq$}
+\newunicodechar{≣}{$\triangleq$}
+\newunicodechar{≃}{$\simeq$}
+\newunicodechar{≅}{$\cong$}
+\newunicodechar{∙}{$\bullet$}
+\newunicodechar{ℓ}{$\ell$}
+\newunicodechar{ℚ}{$\Q$}
+\newunicodechar{ℤ}{$\Z$}
+% \newunicodechar{}{$$}
 
-\newunicodechar{×}{$\times$}
-\newunicodechar{ℓ}{\ensuremath{\mathnormal{\ell}}}
 \newunicodechar{∣}{\ensuremath{\mathnormal{\|}}}
-\newunicodechar{∥}{\ensuremath{\mathnormal{\||}}}
-\newunicodechar{₀}{\ensuremath{{}_0}}
-\newunicodechar{₁}{\ensuremath{{}_1}}
-\newunicodechar{ℚ}{\ensuremath{\mathnormal{\mathbb{Q}}}}
-\newunicodechar{ℤ}{\ensuremath{\mathnormal{\mathbb{Z}}}}
 \newunicodechar{∷}{\ensuremath{::}}
@@
 \author{Guilherme Horta Alvares da Silva}
-\email{guilhermehas@hotmail.com}
+% \email{guilhermehas@hotmail.com}
 \title{Making all equalities equal}
@@
 
--- open import Cubical.Foundations.Prelude
--- open import Cubical.Foundations.Isomorphism
--- open import Cubical.Foundations.Equiv
--- open import Cubical.Foundations.Univalence
--- open import Agda.Primitive
--- open import Cubical.Data.Equality
---
 open import Agda.Primitive.Cubical
@@
 
-\section{Propositional Equality}
+\section{Equalities}
+
+There are multiple ways of defining equalities in a theorem prover.
+In the next sections, they will be defined.
+
+\subsection{Martin-Löf Equality}
 
@@
 
-\section{Cubical Equality}
+\subsection{Cubical Equality}
 
@@
 
-The operator \AgdaBound{~_} revert the interval. If the interval \AgdaBound{i} goes from
-\AgdaBound{i0} to \AgdaBound{i1}, the interval \AgdaBound{~ i} goes from \AgdaBound{i1} to \AgdaBound{i0}.
+The operator TODO-invert revert the interval. If the interval \AgdaBound{i} goes from
+\AgdaBound{i0} to \AgdaBound{i1}, the interval TODO-invert-i goes from \AgdaBound{i1} to \AgdaBound{i0}.
 
-\section{Leibniz equality}
+\subsection{Leibniz equality}
 
@@
 \begin{code}
-module Leibniz {ℓ} {ℓ'} {A : Set ℓ} where
-  _≐_ : (a b : A) → Set
+module LeibnizEquality {ℓ} {ℓ'} {A : Set ℓ} where
+  _≐_ : A → A → Set
   a ≐ b = (P : A → Set ℓ') → P a → P b
@@
 
-%\subsection{}
+\section{Joining all equalities}
+
+All equalities have something in common. They are all equal to each other.
+So it will be defined a common record that all equalities should have.
+In the next defintion, all equalities are equal to the cubical equality:
+
+\begin{code}
+
+open import Cubical.Foundations.Prelude
+open import Cubical.Foundations.Isomorphism
+open import Cubical.Foundations.Equiv
+open import Cubical.Foundations.Univalence
+open import Cubical.Foundations.Function
+open import Cubical.Data.Equality
+
+module _ {a ℓ} {A : Set a} where
+  ≣-Type = A → A → Set ℓ
+
+  record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc (ℓ-max a ℓ)) where
+    constructor eq
+    field
+      ≣-≡-≡ : ∀ {x y} → let
+        ℓ₁ = ℓ-max a ℓ
+
+        x≡y : Type ℓ₁
+        x≡y = x ≡ y
+
+        x≣y : Type ℓ₁
+        x≣y = x ≣ y
+
+        in _≡_ {ℓ-suc ℓ₁} x≣y x≡y
+
+  record Equality : Set (ℓ-suc (ℓ-max a ℓ)) where
+    field
+      _≣_ : ≣-Type
+      isEquality : IsEquality _≣_
+\end{code}
+
+It will be defined for each equality, its instance:
+
+\begin{code}
+module _ {a} {A : Set a} where
+  instance
+    ≡-IsEquality : IsEquality {A = A} _≡_
+    ≡-IsEquality = eq refl
+
+  instance
+    ≡p-IsEquality : IsEquality {A = A} _≡p_
+    ≡p-IsEquality = eq (λ {x y} → sym λ i → p-c {x = x} {y = y} i)
+
+module _ {ℓ} where
+  univalencePath' : {A B : Type ℓ} → (A ≡ B) ≡ (A ≃ B)
+  univalencePath' {A} {B} =
+    ua {ℓ-suc ℓ} {A ≡ B} {A ≃ B} (compEquiv (univalence {ℓ} {A} {B})
+    (isoToEquiv (iso {ℓ} {ℓ-suc ℓ} (λ x → x) (λ x → x) (λ b i → b) λ a i → a)))
+
+  instance
+    ≃-IsEquality : IsEquality {A = Type ℓ} (λ A B → (A ≃ B))
+    ≃-IsEquality = eq λ {A B} → sym λ i → univalencePath' {A = A} {B = B} i
+
+liftIso : ∀ {a b} {A : Type a} {B : Type b} → Iso {a} {b} A B → Iso {ℓ-max a b} {ℓ-max a b} A B
+liftIso {a} f = iso fun inv (λ x i → rightInv x i) (λ x i → leftInv x i)
+  where open Iso f
+
+open import leibniz
+open Leibniz
+
+module FinalEquality {A : Set} where
+  open MainResult A
+
+  ≐≅≡ : ∀ {a b} → Iso (a ≐ b) (a ≡p b)
+  ≐≅≡ = iso j i (ptoc ∘ ji) (ptoc ∘ ij)
+
+  ≐≡≡' : ∀ {a b} → (a ≐ b) ≡c (a ≡p b)
+  ≐≡≡' = let lifted = liftIso ≐≅≡  in isoToPath lifted
+
+  ≐≡≡ : _≐_ {A} ≡c _≡p_
+  ≐≡≡ i x y = ≐≡≡' {x} {y} i
+
+  open IsEquality
+
+  instance
+    ≐-IsEquality : IsEquality {A = A} _≐_
+    ≐-IsEquality = eq λ {x} {y} → ≐≡≡' ∙ λ i → ≡p-IsEquality {ℓ-zero} .≣-≡-≡ {x} {y} i
+\end{code}
 

### 2021-09-09 paper.lagda.tex
solved TODO ~ problem
fixed grammar mistakes

@@
 
-In the begin of Agda and in most theorems proves, the equality is given by Martin-Löf's definition:
+At the begin of Agda and in most theorems proves, equality is given by Martin-Löf's definition:
 
@@
 
-This equality is very covenient in proof assistances like Agda, because it is possible to pattern match using them:
+This equality is very convenient in proof assistances like Agda because it is possible to pattern match using them:
 
@@
 
-To solve this problem, Agda adopted cubical type theory that equality is a function from path to types:
+To solve this problem, Agda adopted cubical type theory that equality is a function from the path to type:
 
@@
 
-The operator TODO-invert revert the interval. If the interval \AgdaBound{i} goes from
-\AgdaBound{i0} to \AgdaBound{i1}, the interval TODO-invert-i goes from \AgdaBound{i1} to \AgdaBound{i0}.
+The operator $\sim$ invert the interval. If the interval \AgdaBound{i} goes from
+\AgdaBound{i0} to \AgdaBound{i1}, the interval $\sim i$ goes from \AgdaBound{i1} to \AgdaBound{i0}.
 
@@
 All equalities have something in common. They are all equal to each other.
-So it will be defined a common record that all equalities should have.
-In the next defintion, all equalities are equal to the cubical equality:
+So it will be defined as a common record that all equalities should have.
+In the next definition, all equalities are equal to cubical equality:
 

### 2021-09-09 paper.lagda.tex
broke lines

@@
     ua {ℓ-suc ℓ} {A ≡ B} {A ≃ B} (compEquiv (univalence {ℓ} {A} {B})
-    (isoToEquiv (iso {ℓ} {ℓ-suc ℓ} (λ x → x) (λ x → x) (λ b i → b) λ a i → a)))
+    (isoToEquiv (iso {ℓ} {ℓ-suc ℓ}
+    (λ x → x) (λ x → x) (λ b i → b) λ a i → a)))
 
   instance
-    ≃-IsEquality : IsEquality {A = Type ℓ} (λ A B → (A ≃ B))
-    ≃-IsEquality = eq λ {A B} → sym λ i → univalencePath' {A = A} {B = B} i
+    ≃-IsEquality : IsEquality
+      {A = Type ℓ} (λ A B → (A ≃ B))
+    ≃-IsEquality = eq λ {A B} → sym
+      λ i → univalencePath' {A = A} {B = B} i
 
-liftIso : ∀ {a b} {A : Type a} {B : Type b} → Iso {a} {b} A B → Iso {ℓ-max a b} {ℓ-max a b} A B
-liftIso {a} f = iso fun inv (λ x i → rightInv x i) (λ x i → leftInv x i)
+liftIso : ∀ {a b} {A : Type a} {B : Type b}
+  → Iso {a} {b} A B → Iso {ℓ-max a b} {ℓ-max a b} A B
+liftIso {a} f = iso fun inv
+  (λ x i → rightInv x i) (λ x i → leftInv x i)
+
   where open Iso f
@@
     ≐-IsEquality : IsEquality {A = A} _≐_
-    ≐-IsEquality = eq λ {x} {y} → ≐≡≡' ∙ λ i → ≡p-IsEquality {ℓ-zero} .≣-≡-≡ {x} {y} i
+    ≐-IsEquality = eq λ {x} {y} → ≐≡≡' ∙
+      λ i → ≡p-IsEquality {ℓ-zero} .≣-≡-≡ {x} {y} i
 \end{code}

### 2021-09-09 slides.lagda.tex
added slides

\documentclass{beamer}

% Use the input encoding UTF-8 and the font encoding T1.
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Support for Agda code.
\usepackage{agda}

% Decrease the indentation of code.
\setlength{\mathindent}{1em}

% Customised setup for certain characters.
\usepackage{newunicodechar}
\newunicodechar{∋}{$\ni$}
% \newunicodechar{·}{$\cdot$}
\newunicodechar{⊢}{$\vdash$}
\newunicodechar{⋆}{${}^\star$}
\newunicodechar{Π}{$\Pi$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{ƛ}{$\lambdabar$}
\newunicodechar{∅}{$\emptyset$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ϕ}{$\Phi$}
\newunicodechar{ψ}{$\Psi$}
\newunicodechar{ρ}{$\rho$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{σ}{$\sigma$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{∥}{$\parallel$}
\newunicodechar{Λ}{$\Lambda$}
\newunicodechar{₀}{$~_0$}
\newunicodechar{₁}{$~_1$}
\newunicodechar{₂}{$~_2$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{Θ}{$\Theta$}
\newunicodechar{∘}{$\circ$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{⊧}{$\models$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{η}{$\eta$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{ξ}{$\xi$}
\newunicodechar{ℕ}{$\mathbb{N}$}
\newunicodechar{ᶜ}{${}^c$}
\newunicodechar{Φ}{$\Phi$}
\newunicodechar{Ψ}{$\Psi$}
\newunicodechar{⊤}{$\top$}
\newunicodechar{≐}{$\doteq$}
\newunicodechar{≣}{$\triangleq$}
\newunicodechar{≃}{$\simeq$}
\newunicodechar{≅}{$\cong$}
\newunicodechar{∙}{$\bullet$}
\newunicodechar{ℓ}{$\ell$}
% \newunicodechar{}{$$}

\newunicodechar{∣}{\ensuremath{\mathnormal{\|}}}
\newunicodechar{∷}{\ensuremath{::}}
\newunicodechar{ℕ}{\ensuremath{\mathnormal{\mathbb{N}}}}
\newunicodechar{ℚ}{\ensuremath{\mathnormal{\mathbb{Q}}}}
\newunicodechar{ℤ}{\ensuremath{\mathnormal{\mathbb{Z}}}}
\newunicodechar{∥}{\ensuremath{\mathnormal{\||}}}

% Support for Greek letters.
\usepackage{alphabeta}

% Disable ligatures that start with '-'. Note that this affects the
% entire document!
\usepackage{microtype}
\DisableLigatures[-]{encoding=T1}

%Information to be included in the title page:
\title{Using quotient types in Agda}
\author{Guilherme Silva}
\institute{Scottish Programming Languages and Verification Summer School}
\date{17th August 2021}

\begin{document}

\frame{\titlepage}

\begin{frame}
  \frametitle{Motivation}
  In simple type theories with quotient types,
  it is possible to create two distinct elements and after
  make them equal.

  One of the best examples is making $ \frac{1}{2} $ and $ \frac{2}{4} $ be equal elements.
\end{frame}

\begin{frame}
  \frametitle{Imports}
  \begin{code}
  {-# OPTIONS --cubical #-}

  open import Cubical.Foundations.Prelude hiding (isProp; isSet)
  open import Cubical.Relation.Nullary using (¬_)

  open import Cubical.Data.Unit
  open import Cubical.Data.Bool
  open import Cubical.Data.Int
  open import Cubical.Data.Nat hiding (_·_)

  private variable
    ℓ ℓ₁ : Level
    A : Set ℓ
    B : Set ℓ₁
    x y z : A
  \end{code}
\end{frame}

\begin{frame}
  \frametitle{Equalities}
  In cubical type theory, equality is a function between from an interval to a set.
  \begin{code}
  tt≡tt : tt ≡ tt
  tt≡tt i = tt

  refl' : (x : A) → x ≡ x
  refl' x i = x
  \end{code}

\end{frame}

\begin{frame}
  \frametitle{Equalities}
  It is also possible to invert the path of equality.
  If the interval i goes from i0 to i1, the interval \~{} i goes from i1 to i0.

  \begin{code}
  sym' : x ≡ y → y ≡ x
  sym' p i = p (~ i)

  ext : (f g : A → B) → (∀ x → f x ≡ g x) → f ≡ g
  ext f g p i x = -- wants that when i = i0, f x
                  --        and when i = i1, g x
                  p x -- is the same of (f x ≡ g x)
                  i
  \end{code}

\end{frame}

\begin{frame}
  \frametitle{The simplest example of quotient types}
  This is an example when two elements of the same data types are equal:
  \begin{code}
  data Bool≡ : Set where
    true false : Bool≡
    t≡f : true ≡ false

  _ : true ≡ false
  _ = t≡f
  \end{code}
\end{frame}

\begin{frame}
  \frametitle{Functions of quotient types}
  Let a function f between elements of Bool≡ and another set, \\
  if $ x \equiv y $, then $ f(x) \equiv f(y) $.
  In this case, $ x $ is true, $ y $ is false and $ f(x) $ is tt.
  \begin{code}
  f : Bool≡ → Unit
  f true    = tt
  f false   = tt
  f (t≡f i) = refl i -- proving that f true ≡ f false

  \end{code}

\end{frame}

\begin{frame}
  \frametitle{Truncation type}

  In truncation type, every element of it is equal.
  Therefore we can define Bool≡ as ∥ Bool ∥.

  \begin{code}
  data ∥_∥ {ℓ} (A : Set ℓ) : Set ℓ where
    ∣_∣ : A → ∥ A ∥
    squash : ∀ (x y : ∥ A ∥) → x ≡ y

  Bool≡' = ∥ Bool ∥
  \end{code}
\end{frame}

\begin{frame}
  \frametitle{Not all equalities are the same}
  In cubical type theory, the equalities are not always the same.
  In this example, the circle is isomorphic (the same) to the integers:
  \begin{code}
  data Circle : Type where
    base : Circle
    loop : base ≡ base
  \end{code}
\end{frame}

\begin{frame}
  \frametitle{Making equalities equal}
  To make the equality equal, it is necessary when declaring a data type to state that it is a set.
  \begin{code}
  isProp : Type ℓ → Type ℓ
  isProp A = (x y : A) → x ≡ y

  isSet : Type ℓ → Type ℓ
  isSet A = (x y : A) → isProp (x ≡ y)
  \end{code}
\end{frame}

\begin{frame}
  \frametitle{Rational Numbers}
  Rational numbers are defined by numerator and a denominator different from zero.
  Two rational numbers $ \frac{p_1}{q_1} $ and $ \frac{p_2}{q_2} $ are equal when $ p_1 \times q_2 \equiv p_2 \times q_1 $
  \begin{code}
  data ℚ : Type where
    _/_[_] : (p : ℤ) (q : ℤ) → ¬ (q ≡ pos 0) → ℚ
    path : ∀ p₁ q₁ p₂ q₂ {pr₁ pr₂} → (p₁ · q₂) ≡ (p₂ · q₁)
      → p₁ / q₁ [ pr₁ ] ≡ p₂ / q₂ [ pr₂ ]
    trunc : isSet ℚ

  _ : ∀ {pr₁ : ¬ (2 ≡ pos 0)} {pr₂ : ¬ (4 ≡ pos 0)}
    → 1 / 2 [ pr₁ ] ≡ 2 / 4 [ pr₂ ]
  _ = path 1 2 2 4 refl
  \end{code}
\end{frame}

\begin{frame}
  \frametitle{Integers}
  Another way to define integers is making the positive and negative zero equals.
  \begin{code}
  data ℤ' : Type where
    pos' : ℕ → ℤ'
    neg' : ℕ → ℤ'
    0+-≡ : pos' 0 ≡ neg' 0
  \end{code}
\end{frame}

\begin{frame}
  \frametitle{Sets}
  One way of defining sets is to create a list where you can swap elements and remove them when they are equal.
  \begin{code}
  infixr 20 _∷_
  data LFSet (A : Type ℓ) : Type ℓ where
    []    : LFSet A
    _∷_   : (x : A) → (xs : LFSet A) → LFSet A
    dup   : ∀ x xs   → x ∷ x ∷ xs ≡ x ∷ xs
    comm  : ∀ x y xs → x ∷ y ∷ xs ≡ y ∷ x ∷ xs
    trunc : isSet (LFSet A)

  _ : tt ∷ tt ∷ [] ≡ tt ∷ []
  _ = dup tt []

  _ : let true∷false : LFSet Bool
          true∷false = true ∷ false ∷ []
      in true∷false ≡ false ∷ true ∷ []
  _ = comm true false []
  \end{code}
\end{frame}

\begin{frame}
  \vspace*{36 pt}
  \begin{center}
  {\Huge Questions?}
  \end{center}
\end{frame}

\end{document}

### 2021-09-09 slides.lagda.tex
fixed grammar and finished slides

@@
 %Information to be included in the title page:
-\title{Using quotient types in Agda}
+\title{Cubical Agda features}
 \author{Guilherme Silva}
-\institute{Scottish Programming Languages and Verification Summer School}
-\date{17th August 2021}
+\date{11th September 2021}
 
@@
 
+\section{Cubical Agda}
+
 \begin{frame}
-  \frametitle{Motivation}
+  \frametitle{New Features}
+  The most important features in Cubical Agda are:
+
+  \begin{itemize}
+    \item New Equality Type
+    \item Quotient types
+  \end{itemize}
+\end{frame}
+
+\section{Equalities}
+
+\begin{frame}
+  \frametitle{Equalities}
+  There are multiple definitions of equalities and the most important are:
+  \begin{itemize}
+    \item Martin-Löf
+    \item Leibniz
+    \item Cubical
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Imports}
+  \begin{code}
+  {-# OPTIONS --cubical #-}
+
+  module slides where
+
+  open import Agda.Primitive.Cubical
+
+  open import Cubical.Data.Unit
+  open import Cubical.Data.Bool
+  open import Cubical.Data.Int
+  open import Cubical.Data.Nat hiding (_·_)
+  open import Cubical.Data.Prod
+  open import Cubical.Foundations.Isomorphism
+  \end{code}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Martin-Löf equality}
+  At the begin of Agda and in most theorems proves, equality is given by Martin-Löf's definition:
+  \begin{code}
+  module Martin-Löf {ℓ} {A : Set ℓ} where
+
+    data _≡_ (x : A) : A → Set ℓ where
+      refl : x ≡ x
+  \end{code}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Martin-Löf pattern match}
+  This equality is very convenient in proof assistances like Agda because it is possible to pattern match using them:
+
+  \begin{code}
+    private variable
+      x y z : A
+
+    sym  : x ≡ y → y ≡ x
+    sym refl = refl
+
+    trans : x ≡ y → y ≡ z → x ≡ z
+    trans refl refl = refl
+  \end{code}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Martin-Löf problem}
+
+  But the problem of this equality is that it does not handle extensionality and other axioms very well:
+
+  \begin{code}
+  module FunExt {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
+    open Martin-Löf
+
+    funExt-Type = {f g : A → B}
+      → ((x : A) → f x ≡ g x) → f ≡ g
+  \end{code}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Cubical Equality}
+  To solve this problem, Agda adopted cubical type theory that equality is a function from the path to type:
+
+  \begin{code}
+  module CubicalEquality {ℓ} {A : Set ℓ} where
+    postulate
+      PathP : (A : I → Set ℓ) → A i0 → A i1 → Set ℓ
+
+    _≡_ : A → A → Set ℓ
+    _≡_ = PathP λ _ → A
+  \end{code}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Cubical Equality Operators}
+  From this equality, I will define reflection, symmetry and extensionality:
+
+  \begin{code}
+  module CubicalResults {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
+    open import Cubical.Core.Primitives
+
+    private variable
+      x y z : A
+
+    refl : x ≡ x
+    refl {x = x} = λ _ → x
+
+    sym : x ≡ y → y ≡ x
+    sym p i = p (~ i)
+
+    funExt : {f g : A → B}
+      → ((x : A) → f x ≡ g x) → f ≡ g
+    funExt p i x = p x i
+  \end{code}
+
+  The operator $\sim$ invert the interval. If the interval \AgdaBound{i} goes from
+  \AgdaBound{i0} to \AgdaBound{i1}, the interval $\sim i$ goes from \AgdaBound{i1} to \AgdaBound{i0}.
+\end{frame}
+
+\begin{frame}
+  \frametitle{Cubical equality computational behavior}
+  Another advantage of cubical equality is that it has a computational behavior.
+  If there is a term that has a type that two types are equal, in this term, there is information of how they are equal.
+  So this term represents the isomorphism of these two types.
+\end{frame}
+
+\begin{frame}
+  \frametitle{Bool example}
+
+  In this example, I will show the equality of two Bools:
+
+  \begin{code}
+  module CubicalIsomorphism where
+    open import Cubical.Foundations.Prelude
+
+    IsoBool : Iso Bool Bool
+    IsoBool = iso not not ¬¬b ¬¬b
+      where
+        ¬¬b : ∀ b → not (not b) ≡ b
+        ¬¬b false = refl
+        ¬¬b true = refl
+
+    Bool≡Bool : Bool ≡ Bool
+    Bool≡Bool = isoToPath IsoBool
+
+    _ : (transport Bool≡Bool false ≡ true)
+      × (transport Bool≡Bool true ≡ false)
+    _ = refl , refl
+
+  \end{code}
+\end{frame}
+
+\section{Quotient Types}
+
+\begin{frame}
+  \frametitle{Quotient Types' Motivation}
   In simple type theories with quotient types,
@@
   \begin{code}
-  {-# OPTIONS --cubical #-}
 
@@
   open import Cubical.Relation.Nullary using (¬_)
-
-  open import Cubical.Data.Unit
-  open import Cubical.Data.Bool
-  open import Cubical.Data.Int
-  open import Cubical.Data.Nat hiding (_·_)
 
@@
   \end{code}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Equalities}
-  In cubical type theory, equality is a function between from an interval to a set.
-  \begin{code}
-  tt≡tt : tt ≡ tt
-  tt≡tt i = tt
-
-  refl' : (x : A) → x ≡ x
-  refl' x i = x
-  \end{code}
-
-\end{frame}
-
-\begin{frame}
-  \frametitle{Equalities}
-  It is also possible to invert the path of equality.
-  If the interval i goes from i0 to i1, the interval \~{} i goes from i1 to i0.
-
-  \begin{code}
-  sym' : x ≡ y → y ≡ x
-  sym' p i = p (~ i)
-
-  ext : (f g : A → B) → (∀ x → f x ≡ g x) → f ≡ g
-  ext f g p i x = -- wants that when i = i0, f x
-                  --        and when i = i1, g x
-                  p x -- is the same of (f x ≡ g x)
-                  i
-  \end{code}
-
 \end{frame}
@@
   In truncation type, every element of it is equal.
-  Therefore we can define Bool≡ as ∥ Bool ∥.
+  Therefore we can define Bool≡ as ∥ Bool ∥:
 
@@
   \frametitle{Making equalities equal}
-  To make the equality equal, it is necessary when declaring a data type to state that it is a set.
+  To make the equality equal, it is necessary when declaring a data type to state that it is a set:
   \begin{code}
@@
   Rational numbers are defined by numerator and a denominator different from zero.
-  Two rational numbers $ \frac{p_1}{q_1} $ and $ \frac{p_2}{q_2} $ are equal when $ p_1 \times q_2 \equiv p_2 \times q_1 $
+  Two rational numbers $ \frac{p_1}{q_1} $ and $ \frac{p_2}{q_2} $ are equal when $ p_1 \times q_2 \equiv p_2 \times q_1 $:
   \begin{code}
@@
   \frametitle{Integers}
-  Another way to define integers is making the positive and negative zero equals.
+  Another way to define integers is making the positive and negative zero equals:
   \begin{code}
@@
   \frametitle{Sets}
-  One way of defining sets is to create a list where you can swap elements and remove them when they are equal.
+  One way of defining sets is to create a list where you can swap elements and remove them when they are equal:
   \begin{code}
@@
 
-\begin{frame}
-  \vspace*{36 pt}
-  \begin{center}
-  {\Huge Questions?}
-  \end{center}
-\end{frame}
-
 \end{document}

### 2021-09-17 paper.lagda.tex
wrote more about equality instances

@@
 
-\AgdaHide{
-\begin{code}
-{-# OPTIONS --cubical --type-in-type #-}
-
-module paper where
-
-open import Agda.Primitive.Cubical
-\end{code}
-}
-
 \maketitle
@@
 In the next sections, they will be defined.
+
+\subsection{Imports}
+
+First, it will be necessary to give some agda arguments:
+
+\begin{code}
+{-# OPTIONS --cubical --cumulativity #-}
+module paper where
+\end{code}
+
+The cubical flag is necessary because we are using cubical equality,
+and the cumulativiy flag is also necessary for level subtyping,
+
+\begin{code}
+open import Agda.Primitive.Cubical using (I; i0; i1)
+\end{code}
+
+This library loads Cubical Agda Primitives as the equality interval.
 
@@
 \begin{code}
-module LeibnizEquality {ℓ} {ℓ'} {A : Set ℓ} where
-  _≐_ : A → A → Set
-  a ≐ b = (P : A → Set ℓ') → P a → P b
+module LeibnizEquality {A : Set} where
+  _≐_ : A → A → Set₁
+  a ≐ b = (P : A → Set) → P a → P b
 \end{code}
@@
 
+\subsection{Cubical Equality}
+
+The simplest example is the cubical equality hence this equality is already equal to itself.
+
 \begin{code}
@@
     ≡-IsEquality = eq refl
+\end{code}
 
+\subsection{Martin-Löf equality}
+
+The proof of Martin-Löf equality is more difficult, but it is already in Cubical library as \AgdaFunction{p-c}.
+
+\begin{code}
   instance
@@
     ≡p-IsEquality = eq (λ {x y} → sym λ i → p-c {x = x} {y = y} i)
+\end{code}
 
+\subsection{Isomorphism}
+
+The isomorphism is an equality between types.
+
+\begin{code}
 module _ {ℓ} where
@@
     (λ x → x) (λ x → x) (λ b i → b) λ a i → a)))
+\end{code}
 
+\AgdaFunction{univalencePath} is already defined in Agda library, but with \AgdaBound{A ≃ B} instead of
+\AgdaBound{Lifted (A ≃ B)}. This change can be done because of the cumulativity flag.
+
+\begin{code}
   instance
     ≃-IsEquality : IsEquality
-      {A = Type ℓ} (λ A B → (A ≃ B))
+      {A = Type ℓ} _≃_
     ≃-IsEquality = eq λ {A B} → sym
       λ i → univalencePath' {A = A} {B = B} i
+\end{code}
 
+\subsection{Leibniz Equality}
+
+The hardest equality to proof that is equalty is the Leibniz Equality.
+
+\begin{code}
 liftIso : ∀ {a b} {A : Type a} {B : Type b}
@@
   (λ x i → rightInv x i) (λ x i → leftInv x i)
+\end{code}
 
+This \AgdaFunction{liftIso} will be used to lift the Isomorphism to types of the same maximum level of both.
+
+\begin{code}
   where open Iso f
@@
 open Leibniz
+\end{code}
 
+It is importing the definition of Leibniz equality made by \cite{abel2020leibniz}.
+In this work, there is already a proof of the isomorphism between the Leibniz and the Martin-Löf equality.
+
+\begin{code}
 module FinalEquality {A : Set} where
@@
   ≐≅≡ = iso j i (ptoc ∘ ji) (ptoc ∘ ij)
+\end{code}
 
-  ≐≡≡' : ∀ {a b} → (a ≐ b) ≡c (a ≡p b)
-  ≐≡≡' = let lifted = liftIso ≐≅≡  in isoToPath lifted
+In Cubical Library, the definition of isomorphism uses cubical equality instead of Martin-Löf equality
+when we have to proof that \AgdaBound{∀ x → from (to x) ≡ x} and \AgdaBound{∀ x → to (from x) ≡ x}.
+\AgdaFunction{ptoc} is necessary to do this convertion from these equalities.
 
-  ≐≡≡ : _≐_ {A} ≡c _≡p_
-  ≐≡≡ i x y = ≐≡≡' {x} {y} i
+\begin{code}
+  ≐≡≡ : ∀ {a b} → (a ≐ b) ≡c (a ≡p b)
+  ≐≡≡ = let lifted = liftIso ≐≅≡  in isoToPath lifted
+\end{code}
 
+Using the univalence and \AgdaFunction{liftIso} defined previously, it is possible to transform the isormorphism
+into an equality.
+
+\begin{code}
   open IsEquality
@@
     ≐-IsEquality : IsEquality {A = A} _≐_
-    ≐-IsEquality = eq λ {x} {y} → ≐≡≡' ∙
+    ≐-IsEquality = eq λ {x} {y} → ≐≡≡ ∙
       λ i → ≡p-IsEquality {ℓ-zero} .≣-≡-≡ {x} {y} i
 \end{code}
+
+The last pass is to join the three equalities between equalities:
+Leibniz to Martin-Löf to cubical equality.
 

### 2021-09-20 paper.lagda.tex
joined equalities
changed to module versioned

@@
 
+\begin{code}
+module Equalities {a ℓ} {A : Set a} where
+  ≣-Type' = ≣-Type {a} {ℓ} {A}
+  open IsEquality
+
+  module _
+    (_≡₁_ : ≣-Type')
+    (_≡₂_ : ≣-Type')
+    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
+    ⦃ eq₂ : IsEquality _≡₂_ ⦄
+    where
+
+    variable
+      x y : A
+
+    alwaysEqual :  x ≡₁ y → x ≡₂ y
+    alwaysEqual p =
+      let joined = eq₁ .≣-≡-≡ ∙ sym (eq₂ .≣-≡-≡)
+      in transport joined p
+
+\end{code}
+
 \section*{Acknowledgements}

### 2021-09-21 paper.lagda.tex
created instances of equality

--- 2021-09-17 paper.lagda.tex
@@
 
+\begin{code}
+module Equalities {a ℓ} {A : Set a} where
+  ≣-Type' = ≣-Type {a} {ℓ} {A}
+
+  module _
+    (_≡₁_ : ≣-Type')
+    (_≡₂_ : ≣-Type')
+    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
+    ⦃ eq₂ : IsEquality _≡₂_ ⦄
+    where
+
+    ℓ₁ = ℓ-max a ℓ
+
+    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
+      constructor eq
+      field
+        ≣-≡-≡ : ∀ {x y} → let
+          x≡y : Type ℓ₁
+          x≡y = x ≡₁ y
+
+          x≣y : Type ℓ₁
+          x≣y = x ≣ y
+
+          in _≡_ {ℓ-suc ℓ₁} x≣y x≡y
+
+      instance
+        isEquality : IsEquality _≣_
+        isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)
+
+    instance
+      ≡₂-Equality₂ : IsEquality₂ _≡₂_
+      ≡₂-Equality₂ = eq (eq₂ .≣-≡-≡ ∙ sym (eq₁ .≣-≡-≡))
+        where open IsEquality
+
+    alwaysEqual : ∀ {x y} →  x ≡₁ y → x ≡₂ y
+    alwaysEqual {x} {y} p =
+      let joined = sym (≣-≡-≡ {x} {y})
+      in transport joined p
+      where open IsEquality₂ ≡₂-Equality₂
+
+    module _
+      (_≡₃_ : ≣-Type {ℓ-suc ℓ₁} {a})
+      ⦃ eq₃ : IsEquality _≡₃_ ⦄
+      where
+
+      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
+        constructor eq
+        field
+          ≣-≡-≡ : ∀ {x y} → let
+            x≡y : Type ℓ₁
+            x≡y = x ≡₁ y
+
+            x≣y : Type ℓ₁
+            x≣y = x ≣ y
+
+            in x≣y ≡₃ x≡y
+
+        instance
+          isEquality₂ : IsEquality₂ _≣_
+          isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)
+
+          isEquality : IsEquality _≣_
+          isEquality = eq (IsEquality₂.≣-≡-≡ isEquality₂ ∙ IsEquality.≣-≡-≡ eq₁)
+
+      instance
+        ≡₂-Equality₃ : IsEquality₃ _≡₂_
+        ≡₂-Equality₃ = eq α
+          where
+            open IsEquality eq₃
+            α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
+            α {x} {y} = let
+              α₁ = ≣-≡-≡ {x ≡₂ y} {x ≡₁ y}
+              α₂ = IsEquality₂.≣-≡-≡ ≡₂-Equality₂ {x} {y}
+              in transport (sym α₁) α₂
+
+\end{code}
+
 \section*{Acknowledgements}

### 2021-09-21 paper.lagda.tex
fixed unicode
added one more symmetric equality

@@
 \newunicodechar{₂}{$~_2$}
+\newunicodechar{₃}{$~_3$}
 \newunicodechar{θ}{$\theta$}
@@
 \newunicodechar{ℤ}{$\Z$}
+\newunicodechar{⦃}{$\{$}
+\newunicodechar{⦄}{$\}$}
 % \newunicodechar{}{$$}
@@
 
+    ≡-≡-≣ : {x y : A} → let
+      x≡y : Type (ℓ-max a ℓ)
+      x≡y = x ≡ y
+      x≣y = x ≣ y
+      in x≡y ≡ x≣y
+    ≡-≡-≣ = sym ≣-≡-≡
+
+  module _ (_≣_ : ≣-Type) where
+    sym-Equality : (≡-≡-≣ : {x y : A} → let
+      x≡y : Type (ℓ-max a ℓ)
+      x≡y = x ≡ y
+      x≣y = x ≣ y
+      in x≡y ≡ x≣y)
+      → IsEquality _≣_
+    sym-Equality ≡-≡-≣ = eq (sym ≡-≡-≣)
+
   record Equality : Set (ℓ-suc (ℓ-max a ℓ)) where
@@
 
+      ≡-≡-≣ : {x y : A} → let
+        x≡y : Type ℓ₁
+        x≡y = x ≡₁ y
+        x≣y = x ≣ y
+        in x≡y ≡ x≣y
+      ≡-≡-≣ = sym ≣-≡-≡
+
       instance
@@
 
+        ≡-≡-≣ : {x y : A} → let
+          x≡y : Type ℓ₁
+          x≡y = x ≡₁ y
+          x≣y = x ≣ y
+          in x≡y ≡₃ x≣y
+        ≡-≡-≣ = let
+          α₁ = IsEquality.≡-≡-≣ eq₃
+          α₂ = IsEquality.≣-≡-≡ eq₁
+          α₃ = IsEquality.≡-≡-≣ isEquality
+          in transport α₁ (α₂ ∙ α₃)
+
       instance

### 2021-09-21 paper.lagda.tex
used sym-Equality

@@
 
-  module _ (_≣_ : ≣-Type) where
+  module _ {_≣_ : ≣-Type} where
     sym-Equality : (≡-≡-≣ : {x y : A} → let
@@
     ≡p-IsEquality : IsEquality {A = A} _≡p_
-    ≡p-IsEquality = eq (λ {x y} → sym λ i → p-c {x = x} {y = y} i)
+    ≡p-IsEquality = sym-Equality (λ {x y} → λ i → p-c {x = x} {y = y} i)
 \end{code}
@@
       {A = Type ℓ} _≃_
-    ≃-IsEquality = eq λ {A B} → sym
+    ≃-IsEquality = sym-Equality λ {A B} →
       λ i → univalencePath' {A = A} {B = B} i
@@
             α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
-            α {x} {y} = let
-              α₁ = ≣-≡-≡ {x ≡₂ y} {x ≡₁ y}
-              α₂ = IsEquality₂.≣-≡-≡ ≡₂-Equality₂ {x} {y}
-              in transport (sym α₁) α₂
+            α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ ≡₂-Equality₂)
 

### 2021-09-21 paper.lagda.tex
added symmetric equality

@@
 
+    module _ {_≣_ : ≣-Type} where
+      sym-Equality₂ : (≡-≡-≣ : {x y : A} → let
+        x≡y : Type (ℓ-max a ℓ)
+        x≡y = x ≡₁ y
+        x≣y = x ≣ y
+        in x≡y ≡ x≣y)
+        → IsEquality₂ _≣_
+      sym-Equality₂ ≡-≡-≣ = eq (sym ≡-≡-≣)
+
     module _
@@
 
+      module _ {_≣_ : ≣-Type'} where
+        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
+          x≡y : Type (ℓ-max a ℓ)
+          x≡y = x ≡₁ y
+          x≣y = x ≣ y
+          in x≡y ≡₃ x≣y)
+          → IsEquality₃ _≣_
+        sym-Equality₃ ≡-≡-≣ = eq (let
+          α₁ = IsEquality.≡-≡-≣ eq₃
+          α₂ = transport (sym α₁) ≡-≡-≣
+          in transport α₁ (sym α₂))
+
 \end{code}

### 2021-09-21 paper.lagda.tex
organized the code

@@
   ≣-Type' = ≣-Type {a} {ℓ} {A}
+  ℓ₁ = ℓ-max a ℓ
 
@@
     (_≡₁_ : ≣-Type')
-    (_≡₂_ : ≣-Type')
     ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
-    ⦃ eq₂ : IsEquality _≡₂_ ⦄
     where
 
-    ℓ₁ = ℓ-max a ℓ
-
-    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
+    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
       constructor eq
@@
         isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)
+
+    module _
+      (_≡₂_ : ≣-Type')
+      ⦃ eq₂ : IsEquality _≡₂_ ⦄
+      where
 
@@
 
-      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
+      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
         constructor eq
@@
 
+      module _
+        (_≡₂_ : ≣-Type')
+        ⦃ eq₂ : IsEquality _≡₂_ ⦄
+        where
+
         instance
@@
               α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
-            α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ ≡₂-Equality₂)
+              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ _≡₂_))
 
@@
           in transport α₁ (sym α₂))
-
 \end{code}

### 2021-09-22 paper.lagda.tex
got leibniz equality from equalities

@@
           in transport α₁ (sym α₂))
+
+module _ {A : Set} where
+  open Equalities {ℓ-zero} {ℓ-suc ℓ-zero} {A}
+
+  _≡p₁_ : A → A → Set₁
+  x ≡p₁ y = x ≡p y
+
+  _ = ≡p-IsEquality
+  instance
+    ≡p₁-isEquality : IsEquality _≡p₁_
+    ≡p₁-isEquality = eq λ {x y} → (sym λ i → let
+      α : Type₁
+      α = p-c {ℓ-zero} {A} {x = x} {y = y} i
+      in α)
+
+  leibniz : IsEquality  (_≐_ {A})
+  leibniz =
+    IsEquality₂.isEquality (eq λ {x y} → FinalEquality.≐≡≡ {_} {x} {y})
+
 \end{code}

### 2021-09-23 paper.lagda.tex
added equality of equalities

--- 2021-09-21 paper.lagda.tex
@@
   ≣-Type = A → A → Set ℓ
+  private
+    ℓ₁ = ℓ-max a ℓ
 
@@
       ≣-≡-≡ : ∀ {x y} → let
-        ℓ₁ = ℓ-max a ℓ
-
         x≡y : Type ℓ₁
@@
   record Equality : Set (ℓ-suc (ℓ-max a ℓ)) where
+    constructor eqC
     field
       _≣_ : ≣-Type
-      isEquality : IsEquality _≣_
+      ⦃ isEquality ⦄ : IsEquality _≣_
+
+  EqFromInstance : {≣ : ≣-Type} → IsEquality ≣ → Equality
+  EqFromInstance inst = eqC _ ⦃ inst ⦄
+
+  eqsEqual : (_≣₁_ _≣₂_ : ≣-Type)
+    ⦃ ≣₁-eq : IsEquality _≣₁_ ⦄
+    ⦃ ≣₂-eq : IsEquality _≣₂_ ⦄
+    → ∀ {x y} → let
+      x≣₁y : Type ℓ₁
+      x≣₁y = x ≣₁ y
+
+      x≣₂y : Type ℓ₁
+      x≣₂y = x ≣₂ y
+
+      in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
+  eqsEqual _≣₁_ _≣₂_ ⦃ eq ≣-≡-≡₁ ⦄ ⦃ eq ≣-≡-≡₂ ⦄ = ≣-≡-≡₁ ∙ sym ≣-≡-≡₂
 \end{code}
@@
     ≡-IsEquality = eq refl
+  ≡-Equality : Equality {_} {a} {A}
+  ≡-Equality = eqC _≡_
+
 \end{code}
@@
     ≡p-IsEquality : IsEquality {A = A} _≡p_
-    ≡p-IsEquality = sym-Equality (λ {x y} → λ i → p-c {x = x} {y = y} i)
+    ≡p-IsEquality = sym-Equality p-c
 \end{code}
@@
       {A = Type ℓ} _≃_
-    ≃-IsEquality = sym-Equality λ {A B} →
-      λ i → univalencePath' {A = A} {B = B} i
+    ≃-IsEquality = sym-Equality univalencePath'
 \end{code}
@@
         sym-Equality₂ : (≡-≡-≣ : {x y : A} → let
-          x≡y : Type (ℓ-max a ℓ)
+          x≡y : Type ℓ₁
           x≡y = x ≡₁ y
@@
           in transport α₁ (sym α₂))
+
+module LeibnizFromPEquality {A : Set} where
+  open Equalities {ℓ-zero} {ℓ-suc ℓ-zero}
+
+  _≡p₁_ : A → A → Set₁
+  x ≡p₁ y = x ≡p y
+
+  instance
+    ≡p₁-isEquality : IsEquality _≡p₁_
+    ≡p₁-isEquality = eq λ {x y} → (sym λ i → let
+      α : Type₁
+      α = p-c {ℓ-zero} {x = x} {y = y} i
+      in α)
+
+  leibniz : IsEquality _≐_
+  leibniz =
+    IsEquality₂.isEquality (eq FinalEquality.≐≡≡)
+
 \end{code}

### 2021-09-23 paper.lagda.tex
refactored the code

@@
       in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
-  eqsEqual _≣₁_ _≣₂_ ⦃ eq ≣-≡-≡₁ ⦄ ⦃ eq ≣-≡-≡₂ ⦄ = ≣-≡-≡₁ ∙ sym ≣-≡-≡₂
+  eqsEqual _ _ ⦃ eq ≣-≡-≡₁ ⦄ ⦃ eq ≣-≡-≡₂ ⦄ = ≣-≡-≡₁ ∙ sym ≣-≡-≡₂
 \end{code}
@@
     ≡-IsEquality = eq refl
-  ≡-Equality : Equality {_} {a} {A}
+  ≡-Equality : Equality {ℓ = a}
   ≡-Equality = eqC _≡_
@@
     ≡p-IsEquality = sym-Equality p-c
+  ≡p-Equality : Equality {ℓ = a}
+  ≡p-Equality = eqC _≡p_
 \end{code}
@@
     ≃-IsEquality = sym-Equality univalencePath'
+  ≃-Equality : Equality {ℓ = ℓ}
+  ≃-Equality = eqC _≃_
 \end{code}
@@
       λ i → ≡p-IsEquality {ℓ-zero} .≣-≡-≡ {x} {y} i
+
+  ≐-Equality : Equality {ℓ = ℓ-suc ℓ-zero}
+  ≐-Equality = eqC _≐_
 \end{code}
@@
 module Equalities {a ℓ} {A : Set a} where
+  private
     ≣-Type' = ≣-Type {a} {ℓ} {A}
@@
   module _
-    (_≡₁_ : ≣-Type')
-    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
+    (Eq₁ : Equality {_} {ℓ} {A})
     where
+
+    open Equality Eq₁ renaming (_≣_ to _≡₁_; isEquality to eq₁)
 
@@
       instance
-        isEquality : IsEquality _≣_
-        isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)
+        ≣-isEquality : IsEquality _≣_
+        ≣-isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)
 
     module _
-      (_≡₂_ : ≣-Type')
-      ⦃ eq₂ : IsEquality _≡₂_ ⦄
+      (Eq₂ : Equality {_} {ℓ} {A})
       where
+
+      open Equality Eq₂ renaming (_≣_ to _≡₂_; isEquality to eq₂)
 
@@
     module _
-      (_≡₃_ : ≣-Type {ℓ-suc ℓ₁} {a})
-      ⦃ eq₃ : IsEquality _≡₃_ ⦄
+      (Eq₃ : Equality {A = Set ℓ₁})
       where
+
+      open Equality Eq₃ renaming (_≣_ to _≡₃_; isEquality to eq₃)
 
@@
         instance
-          isEquality₂ : IsEquality₂ _≣_
-          isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)
+          ≣-isEquality₂ : IsEquality₂ _≣_
+          ≣-isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)
 
-          isEquality : IsEquality _≣_
-          isEquality = eq (IsEquality₂.≣-≡-≡ isEquality₂ ∙ IsEquality.≣-≡-≡ eq₁)
+          ≣-isEquality : IsEquality _≣_
+          ≣-isEquality = eq (IsEquality₂.≣-≡-≡ ≣-isEquality₂ ∙ IsEquality.≣-≡-≡ eq₁)
 
@@
           α₂ = IsEquality.≣-≡-≡ eq₁
-          α₃ = IsEquality.≡-≡-≣ isEquality
+          α₃ = IsEquality.≡-≡-≣ ≣-isEquality
           in transport α₁ (α₂ ∙ α₃)
@@
       module _
-        (_≡₂_ : ≣-Type')
-        ⦃ eq₂ : IsEquality _≡₂_ ⦄
+        (Eq₂ : Equality {_} {ℓ} {A})
         where
+
+        open Equality Eq₂ renaming (_≣_ to _≡₂_; isEquality to eq₂)
 
@@
               α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
-              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ _≡₂_))
+              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ (eqC _≡₂_)))
 
@@
 
-  leibniz : IsEquality _≐_
+  leibniz : IsEquality {A = A} _≐_
   leibniz =
-    IsEquality₂.isEquality (eq FinalEquality.≐≡≡)
+    IsEquality₂.≣-isEquality {Eq₁ = eqC _≡p_} (eq FinalEquality.≐≡≡)
 

### 2021-09-23 paper.lagda.tex
explaneid more the code

@@
 
+\section{New Equalities types}
+
+The equalities used previously were defined using the cubical equality.
+Now I will define them using other equalities.
+
+% \end{code}
+% \begin{code}
+
 \begin{code}
@@
     ℓ₁ = ℓ-max a ℓ
+\end{code}
 
+Loaded the modules using the levels to be more generic.
+
+\begin{code}
   module _
@@
     open Equality Eq₁ renaming (_≣_ to _≡₁_; isEquality to eq₁)
+\end{code}
 
+I am importing a generic equality to use it to define a more generic equality.
+
+\begin{code}
     record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
@@
           x≡y = x ≡₁ y
+\end{code}
 
+Different from previously definition of \AgdaFunction{IsEquality},
+the cubical equality defined in the line above was substituted by
+the more generic equality \AgdaFunction{≡₁}.
+
+\begin{code}
           x≣y : Type ℓ₁
@@
           in _≡_ {ℓ-suc ℓ₁} x≣y x≡y
+\end{code}
 
+The rest of the definition is the same.
+
+\begin{code}
       ≡-≡-≣ : {x y : A} → let

### 2021-09-23 paper.lagda.tex
redefined from previous theorem

@@
 
-% \end{code}
-% \begin{code}
-
 \begin{code}
@@
           in _≡_ {ℓ-suc ℓ₁} x≣y x≡y
-\end{code}
 
-The rest of the definition is the same.
-
-\begin{code}
       ≡-≡-≣ : {x y : A} → let
@@
 
+\end{code}
+
+The rest of the definition is the same.
+
+\begin{code}
       instance
@@
         ≣-isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)
+\end{code}
 
+From a more generic defintion of equality,
+it is easily possible to return to the less generic definition.
+
+\begin{code}
     module _
@@
       open Equality Eq₂ renaming (_≣_ to _≡₂_; isEquality to eq₂)
+\end{code}
+
+I am defining a new generic equality to prove that it is
+an equality of type 2:
+
+% \end{code}
+%
+% \begin{code}
+
+\begin{code}
+
+      eqsEqual₂ : ∀ {x y} → let
+        x≣₁y : Type ℓ₁
+        x≣₁y = x ≡₁ y
+
+        x≣₂y : Type ℓ₁
+        x≣₂y = x ≡₂ y
+
+        in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
+      eqsEqual₂ = eqsEqual _≡₁_ _≡₂_
 
@@
         ≡₂-Equality₂ : IsEquality₂ _≡₂_
-        ≡₂-Equality₂ = eq (eq₂ .≣-≡-≡ ∙ sym (eq₁ .≣-≡-≡))
+        ≡₂-Equality₂ = eq (sym eqsEqual₂)
           where open IsEquality
-
-      alwaysEqual : ∀ {x y} →  x ≡₁ y → x ≡₂ y
-      alwaysEqual {x} {y} p =
-        let joined = sym (≣-≡-≡ {x} {y})
-        in transport joined p
-        where open IsEquality₂ ≡₂-Equality₂
 
@@
         sym-Equality₂ ≡-≡-≣ = eq (sym ≡-≡-≣)
+
+\end{code}
+
+Given a symmetric definition of the previous equality,
+it is easy to prove that it is also an equality of type 2.
+
+\begin{code}
 

### 2021-12-13 paper.lagda.tex
added few things in the code
added private variable

@@
 \newunicodechar{Λ}{$\Lambda$}
-\newunicodechar{₁}{$~_0$}
+\newunicodechar{₀}{$~_0$}
 \newunicodechar{₁}{$~_1$}
@@
 
+  private variable
+    x y z : A
+
   record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc (ℓ-max a ℓ)) where
@@
     field
-      ≣-≡-≡ : ∀ {x y} → let
+      ≣-≡-≡ : let
         x≡y : Type ℓ₁
@@
 
-    ≡-≡-≣ : {x y : A} → let
+    ≡-≡-≣ : let
       x≡y : Type (ℓ-max a ℓ)
@@
     ℓ₁ = ℓ-max a ℓ
+
+  private variable
+    x y z : A
 \end{code}
@@
       field
-        ≣-≡-≡ : ∀ {x y} → let
+        ≣-≡-≡ : let
           x≡y : Type ℓ₁
@@
 
-      ≡-≡-≣ : {x y : A} → let
+      ≡-≡-≣ : let
         x≡y : Type ℓ₁
@@
 \begin{code}
-
-      eqsEqual₂ : ∀ {x y} → let
+      eqsEqual₂ : let
         x≣₁y : Type ℓ₁
@@
         field
-          ≣-≡-≡ : ∀ {x y} → let
+          ≣-≡-≡ : let
             x≡y : Type ℓ₁
@@
 
-        ≡-≡-≣ : {x y : A} → let
+        ≡-≡-≣ : let
           x≡y : Type ℓ₁
@@
               open IsEquality eq₃
-              α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
+              α : (x ≡₂ y) ≡₃ (x ≡₁ y)
               α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ (eqC _≡₂_)))

### 2021-12-13 paper.lagda.tex
Finished the explain of equalities

@@
 
-% \end{code}
-%
-% \begin{code}
-
 \begin{code}
@@
 
+\subsection{Everything is an equality}
+
+In this part, a relation is an equality when it is equal (using a general equality) to a cubical equality.
+
 \begin{code}
@@
         field
-          ≣-≡-≡ : let
-            x≡y : Type ℓ₁
-            x≡y = x ≡₁ y
+          ≣-≡-≡ : (x ≣ y) ≡₃ (x ≡₁ y)
+\end{code}
 
-            x≣y : Type ℓ₁
-            x≣y = x ≣ y
+With this definition of equality, it is possible to prove that if an equality is equal to a cubical equality,
+so it is equal (using the general or cubical equality) to the cubical equality.
 
-            in x≣y ≡₃ x≡y
-
+\begin{code}
         instance
@@
 
-        ≡-≡-≣ : let
-          x≡y : Type ℓ₁
-          x≡y = x ≡₁ y
-          x≣y = x ≣ y
-          in x≡y ≡₃ x≣y
+\end{code}
+
+This is the proof that the symmetric definition of equality is also valid.
+
+\begin{code}
+        ≡-≡-≣ : (x ≡₁ y) ≡₃ (x ≣ y)
         ≡-≡-≣ = let
@@
           in transport α₁ (α₂ ∙ α₃)
+\end{code}
 
+It is possible to proof that a general equality is an equality from this definition:
+
+\begin{code}
       module _
@@
 
+\end{code}
+
+If there is a proof of the symmetrical equality, so it is also an equality from this definition:
+
+\begin{code}
+
       module _ {_≣_ : ≣-Type'} where
-        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
-          x≡y : Type (ℓ-max a ℓ)
-          x≡y = x ≡₁ y
-          x≣y = x ≣ y
-          in x≡y ≡₃ x≣y)
+        sym-Equality₃ :
+          (≡-≡-≣ : ∀ {x y} → (x ≡₁ y) ≡₃ (x ≣ y))
           → IsEquality₃ _≣_
@@
 
+\end{code}
+
+\section{Using the definitions}
+
+The best part of defining all of these stuffs is that it is now easy to proof that Leibniz equality is an equality.
+
+\begin{code}
 module LeibnizFromPEquality {A : Set} where
@@
   x ≡p₁ y = x ≡p y
+\end{code}
 
+I redefined this equality because it must be a set of universe one.
+And because of that, I have to prove again that this is an equality:
+
+\begin{code}
   instance
@@
       in α)
+\end{code}
 
+With just one line of code, it is possible now to prove that Leibniz equality is an equality
+from Martin-Löf Equality.
+
+\begin{code}
   leibniz : IsEquality {A = A} _≐_
-  leibniz =
-    IsEquality₂.≣-isEquality {Eq₁ = eqC _≡p_} (eq FinalEquality.≐≡≡)
-
+  leibniz = IsEquality₂.≣-isEquality {Eq₁ = eqC _≡p_} (eq FinalEquality.≐≡≡)
 \end{code}

### 2021-12-14 paper.lagda.tex
fixed grammar mistakes

@@
 The cubical flag is necessary because we are using cubical equality,
-and the cumulativiy flag is also necessary for level subtyping,
+and the cumulative flag is also necessary for level subtyping,
 
@@
 
-At the begin of Agda and in most theorems proves, equality is given by Martin-Löf's definition:
+At the beginning of Agda and in most theorems proves, equality is given by Martin-Löf's definition:
 
@@
 
-The simplest example is the cubical equality hence this equality is already equal to itself.
+The simplest example is cubical equality hence this equality is already equal in itself.
 
@@
 
-The proof of Martin-Löf equality is more difficult, but it is already in Cubical library as \AgdaFunction{p-c}.
+The proof of Martin-Löf equality is more difficult, but it is already in the Cubical library as \AgdaFunction{p-c}.
 
@@
 
-The isomorphism is an equality between types.
+Isomorphism is equality between types.
 
@@
 \AgdaFunction{univalencePath} is already defined in Agda library, but with \AgdaBound{A ≃ B} instead of
-\AgdaBound{Lifted (A ≃ B)}. This change can be done because of the cumulativity flag.
+\AgdaBound{Lifted (A ≃ B)}. This change can be done because of the cumulative flag.
 
@@
 
-The hardest equality to proof that is equalty is the Leibniz Equality.
+The hardest equality to prove that is equality is the Leibniz Equality.
 
@@
 It is importing the definition of Leibniz equality made by \cite{abel2020leibniz}.
-In this work, there is already a proof of the isomorphism between the Leibniz and the Martin-Löf equality.
+In this work, there is already proof of the isomorphism between Leibniz and Martin-Löf equality.
 
@@
 In Cubical Library, the definition of isomorphism uses cubical equality instead of Martin-Löf equality
-when we have to proof that \AgdaBound{∀ x → from (to x) ≡ x} and \AgdaBound{∀ x → to (from x) ≡ x}.
-\AgdaFunction{ptoc} is necessary to do this convertion from these equalities.
+when we have to prove that \AgdaBound{∀ x → from (to x) ≡ x} and \AgdaBound{∀ x → to (from x) ≡ x}.
+\AgdaFunction{ptoc} is necessary to do this conversion from these equalities.
 
@@
 
-Using the univalence and \AgdaFunction{liftIso} defined previously, it is possible to transform the isormorphism
-into an equality.
+Using the univalence and \AgdaFunction{liftIso} defined previously, it is possible to transform the isomorphism
+into equality.
 
@@
 
-The equalities used previously were defined using the cubical equality.
+The equalities used previously were defined using cubical equality.
 Now I will define them using other equalities.
@@
 
-I am importing a generic equality to use it to define a more generic equality.
+I am importing generic equality to use it to define more generic equality.
 
@@
 
-From a more generic defintion of equality,
+From a more generic definition of equality,
 it is easily possible to return to the less generic definition.
@@
 Given a symmetric definition of the previous equality,
-it is easy to prove that it is also an equality of type 2.
+it is easy to prove that it is also equality of type 2.
 
@@
 
-In this part, a relation is an equality when it is equal (using a general equality) to a cubical equality.
+In this part, a relation is equality when it is equal (using general equality) to cubical equality.
 
@@
 
-With this definition of equality, it is possible to prove that if an equality is equal to a cubical equality,
+With this definition of equality, it is possible to prove that if equality is equal to cubical equality,
 so it is equal (using the general or cubical equality) to the cubical equality.
@@
 
-This is the proof that the symmetric definition of equality is also valid.
+This is proof that the symmetric definition of equality is also valid.
 
@@
 
-It is possible to proof that a general equality is an equality from this definition:
+It is possible to prove that a general equality is equality from this definition:
 
@@
 
-If there is a proof of the symmetrical equality, so it is also an equality from this definition:
+If there is proof of symmetrical equality, so it is also equality from this definition:
 
@@
 
-The best part of defining all of these stuffs is that it is now easy to proof that Leibniz equality is an equality.
+The best part of defining all of this stuff is that it is now easy to prove that Leibniz equality is equality.
 

### 2021-12-18 paper.lagda.tex
code cleaner with private variable

@@
 
+Private variables are required, so it is not necessary to redefine them later as an implicit variable.
+
+\begin{code}
+open import Cubical.Core.Primitives using (Level; ℓ-max)
+
+private variable
+  ℓ ℓ′ : Level
+  A : Set ℓ
+\end{code}
+
 This library loads Cubical Agda Primitives as the equality interval.
@@
 \begin{code}
-module Martin-Löf {ℓ} {A : Set ℓ} where
-
+module Martin-Löf {A : Set ℓ} where
   data _≡_ (x : A) : A → Set ℓ where
@@
 \begin{code}
-module FunExt {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
+module FunExt {A : Set ℓ} {B : Set ℓ′} where
   open Martin-Löf
@@
 \begin{code}
-module CubicalEquality {ℓ} {A : Set ℓ} where
+module CubicalEquality {A : Set ℓ} where
   postulate
@@
 \begin{code}
-module CubicalResults {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
+module CubicalResults {A : Set ℓ} {B : Set ℓ′} where
   open import Cubical.Core.Primitives
@@
 
-module _ {a ℓ} {A : Set a} where
+module _ {ℓ} {A : Set ℓ′} where
   ≣-Type = A → A → Set ℓ
   private
-    ℓ₁ = ℓ-max a ℓ
+    ℓ₁ = ℓ-max ℓ′ ℓ
 
@@
 
-  record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc (ℓ-max a ℓ)) where
+  record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc ℓ₁) where
     constructor eq
@@
     ≡-≡-≣ : let
-      x≡y : Type (ℓ-max a ℓ)
+      x≡y : Type ℓ₁
       x≡y = x ≡ y
@@
     sym-Equality : (≡-≡-≣ : {x y : A} → let
-      x≡y : Type (ℓ-max a ℓ)
+      x≡y : Type ℓ₁
       x≡y = x ≡ y
@@
 
-  record Equality : Set (ℓ-suc (ℓ-max a ℓ)) where
+  record Equality : Set (ℓ-suc ℓ₁) where
     constructor eqC
@@
 \begin{code}
-liftIso : ∀ {a b} {A : Type a} {B : Type b}
-  → Iso {a} {b} A B → Iso {ℓ-max a b} {ℓ-max a b} A B
-liftIso {a} f = iso fun inv
+liftIso : {A : Type ℓ} {B : Type ℓ′}
+  → Iso {ℓ} {ℓ′} A B → Iso {ℓ-max ℓ ℓ′} {ℓ-max ℓ ℓ′} A B
+liftIso f = iso fun inv
   (λ x i → rightInv x i) (λ x i → leftInv x i)
@@
   open MainResult A
+  private variable
+    x y z : A
 
-  ≐≅≡ : ∀ {a b} → Iso (a ≐ b) (a ≡p b)
+  ≐≅≡ : Iso (x ≐ y) (x ≡p y)
   ≐≅≡ = iso j i (ptoc ∘ ji) (ptoc ∘ ij)
@@
 \begin{code}
-  ≐≡≡ : ∀ {a b} → (a ≐ b) ≡c (a ≡p b)
+  ≐≡≡ : (x ≐ y) ≡c (x ≡p y)
   ≐≡≡ = let lifted = liftIso ≐≅≡  in isoToPath lifted
@@
 
-        x≣₂y : Type ℓ₁
-        x≣₂y = x ≡₂ y
-
-        in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
+        in x≣₁y ≡ (x ≡₂ y)
       eqsEqual₂ = eqsEqual _≡₁_ _≡₂_
@@
           x≡y = x ≡₁ y
-          x≣y = x ≣ y
-          in x≡y ≡ x≣y)
+          in x≡y ≡ (x ≣ y))
           → IsEquality₂ _≣_

### 2021-12-18 paper.lagda.tex
changed unicode character

@@
 private variable
-  ℓ ℓ′ : Level
+  ℓ ℓ' : Level
   A : Set ℓ
@@
 \begin{code}
-module FunExt {A : Set ℓ} {B : Set ℓ′} where
+module FunExt {A : Set ℓ} {B : Set ℓ'} where
   open Martin-Löf
@@
 \begin{code}
-module CubicalResults {A : Set ℓ} {B : Set ℓ′} where
+module CubicalResults {A : Set ℓ} {B : Set ℓ'} where
   open import Cubical.Core.Primitives
@@
 
-module _ {ℓ} {A : Set ℓ′} where
+module _ {ℓ} {A : Set ℓ'} where
   ≣-Type = A → A → Set ℓ
   private
-    ℓ₁ = ℓ-max ℓ′ ℓ
+    ℓ₁ = ℓ-max ℓ' ℓ
 
@@
 \begin{code}
-liftIso : {A : Type ℓ} {B : Type ℓ′}
-  → Iso {ℓ} {ℓ′} A B → Iso {ℓ-max ℓ ℓ′} {ℓ-max ℓ ℓ′} A B
+liftIso : {A : Type ℓ} {B : Type ℓ'}
+  → Iso {ℓ} {ℓ'} A B → Iso {ℓ-max ℓ ℓ'} {ℓ-max ℓ ℓ'} A B
 liftIso f = iso fun inv
